### 2017-05-31 doc/response.tex

\newpage
\pagenumbering{roman}

\noindent
Dear Dr.~Merlo,
\newline

Thank you for the very helpful suggestions and insightful questions
posed in this review.  We apologize for the delay getting this
revision back to you and very much appreciate the extension you 
gave us to resubmit the manuscript.

We have substantially revised the article in response to your and the reviewers' 
comments. Specifically with regard to the two main issues you raised, we have 
introduced a uni-modal language model (referred to as the {\sc LM} model in the text) 
and reported the results of the experiments on this model as well. Also following 
your recommendation, we have removed the exploratory parts of (the old) Section 6, 
and reorganized the paper by merging previous Sections 4, 5 and the remaining of 
Section 6 into a single section containing all the experiments (that is Section 4 in the 
revised manuscript). We have kept and expanded the quantitative analysis of the nature of 
n-gram contexts that trigger individual dimensions in the hidden layers; this experiment is 
now reported in Section~\ref{sec:contexts}.

Furthermore, we have made clarifications about the details of the techniques all 
through the manuscript, expanded Introduction (Section~\ref{sec:intro}) to 
emphasise our contributions, updated Related Work (Section~\ref{sec:related}) 
to include relevant papers that came out while this manuscript was under review, and expanded Discussion (Section~\ref{sec:conclusion}) to discuss in more detail the relevance and generalizability of our techniques. 
We reran all the experiments with a different, more reliable parser,
which caused minor differences in the details of the figures.

@@

2 What is this paper about? [Help]
: 
This paper presents an analysis of the information learned by
recurrent neural networks. It focuses on one particular multimodal,
multitask model, Imaginet, which is trained on images and their
descriptions. The paper proposes a new measure, the omission score,
which indicates how sensitive the network is to individual words in
the input. Using this method, the authors show that the textual module
of the model pays attention to function words, while the visual module
pays attention to content words. The authors then propose a second
method which can be used to analyze which n-grams the hidden units of
the model are sensitive to; this results in meaningful syntactic and
semantic clusters. This time, there is no clear-cut distinction
between textual and visual modules.

3 Strengths and Weaknesses [Help]

Strengths:
: 
This paper makes a useful methodological contribution by proposing
methods to analyze the knowledge learned by neural networks, which is
an underexplored area, at least for networks trained on text data. The
paper is well written, and technically sound.

Weaknesses:
: 
The results of the paper are unfortunately fairly obvious. From the
omission score analysis, we learn that a model trained to predict the
next word in a sentence is sensitive to function words, while a word
trained to associate a sentence with an image representation (which is
essentially the output of the object detector) pays more attention to
nouns. This is not at all surprising, it just reflects the different
training objectives. The fact that the hidden units respond to
specific n-grams is also expected; most people already believe that
RNNs are good at approximating n-gram models; the question is, can
they model more elaborate syntactic structures?
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  
The results from Figure~\ref{fig:omission-imaginet} are indeed
unsurprising. We should expect any method which works well to recover
such expected results. In addition, there are, however, other findings
which we consider far from obvious: for example the fact that the
{\sc Visual} pathway assigns very different importance to the same
word type in different grammatical functions (see See
Section~\ref{sec:beyondlexical}). We have tried to highlight the
non-trivial insights more in the paper.

### 2017-05-31 doc/categories.tex

For other RNN architectures such as LSTMs \label{edit:omitgeneral}
and their bi-directional variants, measuring the contribution
of tokens to their predictions (or the omission scores)
can be straight-forwardly computed using their hidden state 
at the last time step used for prediction. Furthermore, the technique 
can be applied in general to other architectures which
map variable length linguistic expressions to the same fixed dimensional
space and perform predictions based on these embeddings. 
This includes tree-structured Recursive Neural Network models such as the Tree-LSTM
introduced in \namecite{kai2015treelstm} or the CNN architecture of \namecite{yoonneural2014} 
for sentence classification. In both cases the pre-softmax activations can be extracted 
from the models as the representations of the full and partial sentences.

@@

Models that utilize the sequential structure of language 
have the capacity to interpret the same word-type differently depending on
the context. The omission score distributions in Section \ref{sec:omitimaginet} 
show that in the case of {\sc Imaginet} the 
pathways are differentially sensitive to content vs.\ function
words. In principle, this may be either just due to purely lexical features or the model 
may actually learn to pay more attention to the same word type in appropriate
contexts. This section investigates to what extent our models
discriminate between occurrences of a given word in different positions and 
grammatical functions. The analysis we described here takes \label{edit:beyonlexicalgeneral}
the omission scores as input data, therefore it can be potentially applied 
to any architecture for which the omission scores can be computed. However,
the presented analysis and results regarding word positions can only be meaningful
for Recurrent Neural Networks as they compute their representations sequentially and are not
limited by fixed window sizes.\footnote{CNNs with multi-word filters
and tree-structured recursive neural networks do not incrementally build representations
of sentences in a left-to-right or right-to-left fashion. 
Bi-directional RNNs, on the other hand, are sensitive by word-order and can potentially
learn to handle the same word in different positions differently. \label{edit:foot}}

>>>>

%For other RNN architectures such as LSTMs \label{edit:omitgeneral}
%and their bi-directional variants, measuring the contribution
%of tokens to their predictions (or the omission scores)
%can be straight-forwardly computed using their hidden state 
%at the last time step used for prediction. Furthermore, the technique 
%can be applied in general to other architectures which
%map variable length linguistic expressions to the same fixed dimensional
%space and perform predictions based on these embeddings. 
%This includes tree-structured Recursive Neural Network models such as the Tree-LSTM
%introduced in \namecite{kai2015treelstm} or the CNN architecture of \namecite{yoonneural2014} 
%for sentence classification. In both cases the pre-softmax activations can be extracted 
%from the models as the representations of the full and partial sentences.

@@

Models that utilize the sequential structure of language 
have the capacity to interpret the same word-type differently depending on
the context. The omission score distributions in Section \ref{sec:omitimaginet} 
show that in the case of {\sc Imaginet} the 
pathways are differentially sensitive to content vs.\ function
words. In principle, this may be either just due to purely lexical features or the model 
may actually learn to pay more attention to the same word type in appropriate
contexts. This section investigates to what extent our models
discriminate between occurrences of a given word in different positions and 
grammatical functions.

%The analysis we described here takes
%the omission scores as input data, therefore it can be potentially applied 
%to any architecture for which the omission scores can be computed. However,
%the presented analysis and results regarding word positions can only be meaningful
%for Recurrent Neural Networks as they compute their representations sequentially and are not
%limited by fixed window sizes.\footnote{CNNs with multi-word filters
%and tree-structured recursive neural networks do not incrementally build representations
%of sentences in a left-to-right or right-to-left fashion. 
%Bi-directional RNNs, on the other hand, are sensitive by word-order and can potentially
%learn to handle the same word in different positions differently. \label{edit:foot}}
